\begin{titlepage} % with this page count is reset when we end environment
    \pagenumbering{gobble} % hide page numbers

    \begin{center}
        \fontsize{28}{36}\selectfont % changes font size

        Generation and Applications of Knowledge Graphs in Systems and Networks Biology

        \vspace{3.5cm} % adds vertical space
        \renewcommand{\baselinestretch}{1.5} % sets line separation
        \large

        Kumulative Dissertation \\
        zur Erlangung des Doktorgrades (Dr. rer. nat.)\\
        der Mathematisch-Naturwissenschaftlichen Fakult\"at \\
        der Rheinischen Friedrich-Wilhelms-Universit\"at Bonn \\

        \vspace{2.0cm}
        \renewcommand{\baselinestretch}{1.1}

        vorgelegt von \\
        \textsc{Charles Tapley Hoyt} \\
        aus New Haven, United States of America \\

        \renewcommand{\baselinestretch}{1}
        \vspace{1.0cm}

        Bonn, 2019 \\
    \end{center}
\end{titlepage}

\newpage\null\newpage

\begin{flushleft} % supresses indentation in the first line of a paragraph
    \vspace*{12cm}
    \large

    Angefertigt mit Genehmigung \\
    der Mathematisch-Naturwissenschaftlichen Fakult\"at \\
    der Rheinischen Friedrich-Wilhelms-Universit\"at Bonn \\

    \vspace{1.5cm}
    \renewcommand{\baselinestretch}{1.6}

    \begin{enumerate}
        \item Gutachter: Univ.-Prof. Dr. rer. nat. Martin Hofmann-Apitius
        \item Gutachter: Univ.-Prof. Dr. rer. nat. Andreas Weber
    \end{enumerate}
    Tag der Promotion: XX. September 2019 \\
    Erscheinungsjahr: 2019 \\

\end{flushleft}
\newpage\null\newpage

% \input{others/abstract}

\setlength{\parskip}{1em} % set space between paragraphs
\renewcommand{\baselinestretch}{1.2} % set line spacing

% \input{others/acknowledgement}

\chapter*{Publications}

\section*{Thesis Publications}

\begin{enumerate}
    \item \textbf{Hoyt, C. T.}, Konotopez, A., \& Ebeling, C. (2017). PyBEL: a computational framework for Biological Expression Language. \textit{Bioinformatics (Oxford, England)}, 34(4), 703–704.
    \item \textbf{Hoyt, C. T.}, Domingo-Fern\'{a}ndez, D., \& Hofmann-Apitius, M. (2018). BEL Commons: an environment for exploration and analysis of networks encoded in Biological Expression Language. \textit{Database}, 2018(3), 1–11.
    \item \textbf{Hoyt, C. T.}, \textit{et al.} (2019). Re-curation and rational enrichment of knowledge graphs in Biological Expression Language. \textit{Database}, 2019, baz068.
    \item \textbf{Hoyt, C. T.}, \textit{et al.} (2019). Bio2BEL: Integration of Structured Knowledge Sources with Biological Expression Language. \textit{BMC Bioinformatics, submitted}.
    \item Gündel, M., \textbf{Hoyt, C. T.}, \& Hofmann-Apitius, M. (2018). BEL2ABM: Agent-based simulation of static models in Biological Expression Language. \textit{Bioinformatics}, 34(13), 2316–2318.
    \item Muslu, Ö., \textbf{Hoyt, C. T.}, Hofmann-Apitius, M., \& Fröhlich, H. (2019). GuiltyTargets: Prioritization of Novel Therapeutic Targets with Deep Network Representation Learning. \textit{IEEE/ACM Trans. Comput. Biol. Bioinform., submitted}.
    \item \textbf{Hoyt, C. T.}, \textit{et al.} (2018). A systematic approach for identifying shared mechanisms in epilepsy and its comorbidities. \textit{Database}, 2018(1).
\end{enumerate}

\section*{Other Publications}

\begin{itemize}
    \item Bradford, R., Sturm, T., Weber, A., Davenport, J. H., England, M., Errami, H., Gerdt, V., Grigoriev, D., \textbf{Hoyt, C. T.}, Košta, M., \& Radulescu, O. (2017). A Case Study on the Parametric Occurrence of Multiple Steady States. In Proceedings of the 2017 ACM on International Symposium on Symbolic and Algebraic Computation - ISSAC ’17 (Vol. Part F1293, pp. 45–52). New York, New York, USA: ACM Press.
    \item Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, Alvarez, C. B., Marin-Llao, J., \& Hofmann-Apitius, M. (2018). ComPath: an ecosystem for exploring, analyzing, and curating mappings across pathway databases. \textit{Npj Systems Biology and Applications}, 5(1), 3.
    \item Domingo-Fern\'{a}ndez, D., Mubeen, S., Marín-Llaó, J., \textbf{Hoyt, C. T.}, \& Hofmann-Apitius, M. (2019). PathMe: merging and exploring mechanistic pathway knowledge. \textit{BMC Bioinformatics}, 20(1), 243.
    \item Ali, M., \textbf{Hoyt, C. T.}, Domingo-Fern\'{a}ndez, D., Lehmann, J., \& Jabeen, H. (2019). BioKEEN: A library for learning and evaluating biological knowledge graph embeddings. \textit{Bioinformatics (Oxford, England)}.
    \item Bradford, R., Davenport, J. H., England, M., Errami, H., Gerdt, V., Grigoriev, D., \textbf{Hoyt, C. T.}, Kosta, M., Radulescu, O., Sturm, T., \& Weber, A. (2019). Identifying the Parametric Occurrence of Multiple Steady States for some Biological Networks. Retrieved from http://arxiv.org/abs/1902.04882
    \item Brito, E., Bogdan Georgiev, B. Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, \& Bauckhage, C. (2019) RatVec: A General Approach for Low-dimensional Distributed Vector Representations via Domain-specific Rational Kernels. \textit{In Proceedings of ECML PKDD}
    \item Ali., M., Jabeen, H., \textbf{Hoyt, C. T.}, \& Lehmann, J. (2019) The KEEN Universe: An Ecosystem for Knowledge Graph Embeddings with a Focus on Reproducibility and Transferability. \textit{In Proceedings of ISWC}.
    \item Ali., M., Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, \& Lehmann, J. (2019) Predicting Missing Links Using PyKEEN. \textit{In Proceedings of ISWC}.
    \item Karki, K., Kodamullil, A. T., \textbf{Hoyt, C. T.}, \& Hofmann-Apitius, M. (2019) Quantifying mechanisms in neurodegenerative diseases (NDDs) using candidate mechanism perturbation amplitude (CMPA) algorithm. \textit{BMC Bioinformatics, submitted}.
    \item Emon, M. A., Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, \& Hofmann-Apitius, M. (2019) PS4DR: a multimodal workflow for identification and prioritization of drugs based on pathway signatures. \textit{BMC Bioinformatics, submitted}.
    \item Mubeen, S., \textbf{Hoyt, C. T.}, Gem\"{u}nd, A., Hofmann-Apitius, M., Fr\"{o}hlich, H., \& Domingo-Fern\'{a}ndez, D. (2019). The Impact of Pathway Database Choice on Statistical Enrichment Analysis and Predictive Modeling. \textit{Bioinformatics (Oxford, England), submitted}.
\end{itemize}

\tableofcontents
\listoffigures
\listoftables
