\chapter*{Publications}

\section*{Thesis Publications}

\input{others/publications_text}

\section*{Other Publications}

\begin{itemize}
    \item Bradford, R., Sturm, T., Weber, A., Davenport, J. H., England, M., Errami, H., Gerdt, V., Grigoriev, D., \textbf{Hoyt, C. T.}, Košta, M., \& Radulescu, O. (2017). A Case Study on the Parametric Occurrence of Multiple Steady States. In Proceedings of the 2017 ACM on International Symposium on Symbolic and Algebraic Computation - ISSAC ’17 (Vol. Part F1293, pp. 45–52). New York, New York, USA: ACM Press.
    \item Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, Alvarez, C. B., Marin-Llao, J., \& Hofmann-Apitius, M. (2018). ComPath: an ecosystem for exploring, analyzing, and curating mappings across pathway databases. \textit{Npj Systems Biology and Applications}, 5(1), 3.
    \item Domingo-Fern\'{a}ndez, D., Mubeen, S., Marín-Llaó, J., \textbf{Hoyt, C. T.}, \& Hofmann-Apitius, M. (2019). PathMe: merging and exploring mechanistic pathway knowledge. \textit{BMC Bioinformatics}, 20(1), 243.
    \item Ali, M., \textbf{Hoyt, C. T.}, Domingo-Fern\'{a}ndez, D., Lehmann, J., \& Jabeen, H. (2019). BioKEEN: A library for learning and evaluating biological knowledge graph embeddings. \textit{Bioinformatics (Oxford, England)}.
    \item Bradford, R., Davenport, J. H., England, M., Errami, H., Gerdt, V., Grigoriev, D., \textbf{Hoyt, C. T.}, Kosta, M., Radulescu, O., Sturm, T., \& Weber, A. (2019). Identifying the Parametric Occurrence of Multiple Steady States for some Biological Networks. Retrieved from http://arxiv.org/abs/1902.04882
    \item Brito, E., Bogdan Georgiev, B. Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, \& Bauckhage, C. (2019) RatVec: A General Approach for Low-dimensional Distributed Vector Representations via Domain-specific Rational Kernels. \textit{In Proceedings of ECML PKDD}
    \item Ali., M., Jabeen, H., \textbf{Hoyt, C. T.}, \& Lehmann, J. (2019) The KEEN Universe: An Ecosystem for Knowledge Graph Embeddings with a Focus on Reproducibility and Transferability. \textit{In Proceedings of ISWC}.
    \item Ali., M., Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, \& Lehmann, J. (2019) Predicting Missing Links Using PyKEEN. \textit{In Proceedings of ISWC}.
    \item Karki, K., Kodamullil, A. T., \textbf{Hoyt, C. T.}, \& Hofmann-Apitius, M. (2019) Quantifying mechanisms in neurodegenerative diseases (NDDs) using candidate mechanism perturbation amplitude (CMPA) algorithm. \textit{BMC Bioinformatics, submitted}.
    \item Emon, M. A., Domingo-Fern\'{a}ndez, D., \textbf{Hoyt, C. T.}, \& Hofmann-Apitius, M. (2019) PS4DR: a multimodal workflow for identification and prioritization of drugs based on pathway signatures. \textit{BMC Bioinformatics, submitted}.
    \item Mubeen, S., \textbf{Hoyt, C. T.}, Gem\"{u}nd, A., Hofmann-Apitius, M., Fr\"{o}hlich, H., \& Domingo-Fern\'{a}ndez, D. (2019). The Impact of Pathway Database Choice on Statistical Enrichment Analysis and Predictive Modeling. \textit{Bioinformatics (Oxford, England), submitted}.
\end{itemize}